---
title: "&nbsp;"
#author: "Ben Tonelli"
#date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(readr)
library(dggridR)
year_target <- 2022
```

## Supplemental Data 2 - Spatiotemporal weather anomaly maps

Below are maps showing spatiotemporal anomaly maps for each climate variable included in the analysis (temperature, snowpack, and precipitation) for the spring arrival period during 2022. Each map represents a different day in the arrival period. Map grid cells are colored according to the 29-day anomaly. Temperature and snowpack show more spatial and temporal autocorrelation in comparison to precipitation. 

These maps can be recreated using the "enviro_spatial_corr.Rmd" for any year included in the analysis.

### Temperature
```{r, fig.show="hold", out.width="50%",echo=FALSE}
# Code to look at spatial correlations in temp, swe and prcp during the study period
data_mdl <- readRDS("ms_data2.rds")
env_cl <- readRDS("enviro_by_cell.rds")

season_interest <- round(seq(min(data_mdl$arr_GAM_mean),max(data_mdl$arr_GAM_mean),by=7))

hexgrid6 <- dggridR::dgconstruct(res = 6) 
countries <- map_data("world")
states <- map_data("state")
countries <- filter(countries,long < -40)
lakes <- map_data("lakes") %>% filter(long < -40)

for (each_day in season_interest){
  day_data <- filter(env_cl, year == year_target & day == each_day)
  
  grid  <- dgcellstogrid(hexgrid6,day_data$cell,frame=TRUE,wrapcells=TRUE)
  grid  <- merge(grid,day_data,by.x="cell",by.y="cell")
  
  ### Plot skeleton ####
  p1 <- ggplot() + coord_map("mollweide",xlim=c(-145,-65),ylim=c(25,65)) + ggtitle(paste("Year=",year_target,"Day=",each_day,sep=" ")) +
    geom_polygon(data=countries, aes(x=long, y=lat, group=group),alpha=1,fill="grey80") +
    geom_polygon(data=lakes, aes(x=long, y=lat, group=group),alpha=1,fill="white") +
    geom_polygon(data=grid,      aes(x=long, y=lat, group=group, fill=anom_tmin_c29), alpha=1)    +
    geom_path   (data=grid,      aes(x=long, y=lat, group=group), alpha=0.4, color="white") +
    geom_path(data=lakes, aes(x=long, y=lat, group=group),alpha=1,color="black") +
    geom_path(data=countries, aes(x=long, y=lat, group=group),alpha=1,color="black") +
    #geom_polygon(data=states, aes(x=long, y=lat, group=group), alpha=.4,fill="grey90", color="darkgrey") +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),
          axis.ticks.y = element_blank(),axis.text.y = element_blank(),
          axis.title.x=element_blank(),axis.title.y=element_blank(),
          plot.margin = unit(c(0, 0, 0, 0), "null"),
          panel.spacing = unit(c(0, 0, 0, 0), "null"),
          legend.key.size = unit(1.25, 'cm'),
          legend.title=element_text(size=22), 
          legend.text=element_text(size=22),
          legend.position = c(.15,.4)) +
    theme(panel.background = element_rect(fill = alpha("white",.5))) +
    scale_fill_gradient2(low="dodgerblue4", mid="grey",high="firebrick4",
                         name = "",midpoint=0,lim=c(-3,3))
  print(p1)
}
```

### Snowpack
```{r, fig.show="hold", out.width="50%",echo=FALSE}
for (each_day in season_interest){
  day_data <- filter(env_cl, year == year_target & day == each_day & !is.na(anom_swe_c29))
  
  grid  <- dgcellstogrid(hexgrid6,day_data$cell,frame=TRUE,wrapcells=TRUE)
  grid  <- merge(grid,day_data,by.x="cell",by.y="cell")
  
  ### Plot skeleton ####
  p1 <- ggplot() + coord_map("mollweide",xlim=c(-145,-65),ylim=c(25,65)) + ggtitle(paste("Year=",year_target,"Day=",each_day,sep=" ")) +
    geom_polygon(data=countries, aes(x=long, y=lat, group=group),alpha=1,fill="grey80") +
    geom_polygon(data=lakes, aes(x=long, y=lat, group=group),alpha=1,fill="white") +
    geom_polygon(data=grid,      aes(x=long, y=lat, group=group, fill=anom_swe_c29), alpha=1)    +
    geom_path   (data=grid,      aes(x=long, y=lat, group=group), alpha=0.4, color="white") +
    geom_path(data=lakes, aes(x=long, y=lat, group=group),alpha=1,color="black") +
    geom_path(data=countries, aes(x=long, y=lat, group=group),alpha=1,color="black") +
    #geom_polygon(data=states, aes(x=long, y=lat, group=group), alpha=.4,fill="grey90", color="darkgrey") +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),
          axis.ticks.y = element_blank(),axis.text.y = element_blank(),
          axis.title.x=element_blank(),axis.title.y=element_blank(),
          plot.margin = unit(c(0, 0, 0, 0), "null"),
          panel.spacing = unit(c(0, 0, 0, 0), "null"),
          legend.key.size = unit(1.25, 'cm'),
          legend.title=element_text(size=22), 
          legend.text=element_text(size=22),
          legend.position = c(.15,.4)) +
    theme(panel.background = element_rect(fill = alpha("white",.5))) +
    scale_fill_gradient2(low="wheat3", mid="grey",high="skyblue4",
                         name = "",midpoint=0,lim=c(-2,3))
  print(p1)
}
```

### Precipitation
```{r, fig.show="hold", out.width="50%",echo=FALSE}
#pdf("prcp_corr_plots.pdf")
for (each_day in season_interest){
  day_data <- filter(env_cl, year == year_target & day == each_day)
  
  grid  <- dgcellstogrid(hexgrid6,day_data$cell,frame=TRUE,wrapcells=TRUE)
  grid  <- merge(grid,day_data,by.x="cell",by.y="cell")
  
  ### Plot skeleton ####
  p1 <- ggplot() + coord_map("mollweide",xlim=c(-145,-65),ylim=c(25,65)) + ggtitle(paste("Year=",year_target,"Day=",each_day,sep=" ")) +
    geom_polygon(data=countries, aes(x=long, y=lat, group=group),alpha=1,fill="grey80") +
    geom_polygon(data=lakes, aes(x=long, y=lat, group=group),alpha=1,fill="white") +
    geom_polygon(data=grid,      aes(x=long, y=lat, group=group, fill=anom_prcp_c29), alpha=1)    +
    geom_path   (data=grid,      aes(x=long, y=lat, group=group), alpha=0.4, color="white") +
    geom_path(data=lakes, aes(x=long, y=lat, group=group),alpha=1,color="black") +
    geom_path(data=countries, aes(x=long, y=lat, group=group),alpha=1,color="black") +
    #geom_polygon(data=states, aes(x=long, y=lat, group=group), alpha=.4,fill="grey90", color="darkgrey") +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
    theme(axis.ticks.x = element_blank(),axis.text.x = element_blank(),
          axis.ticks.y = element_blank(),axis.text.y = element_blank(),
          axis.title.x=element_blank(),axis.title.y=element_blank(),
          plot.margin = unit(c(0, 0, 0, 0), "null"),
          panel.spacing = unit(c(0, 0, 0, 0), "null"),
          legend.key.size = unit(1.25, 'cm'),
          legend.title=element_text(size=22), 
          legend.text=element_text(size=22),
          legend.position = c(.15,.4)) +
    theme(panel.background = element_rect(fill = alpha("white",.5))) +
    scale_fill_gradient2(low="wheat3", mid="grey",high="darkgreen",
                         name = "",midpoint=0,lim=c(-3,3))
  print(p1)
}
```
